---
title: "Plotly examples"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Create interactive graphics using plot.ly and design a data dashboard using flexdashboard.


### Examples of plotly

We're gona look at NYC Airbnb data.
```{r}
library(tidyverse)
library("p8105.datasets")
library(plotly)
```


```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>% # let dataset smaller
  select(neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>% 
  filter(
    neighbourhood_group == "Manhattan",
    price  %in% 100:500,
    room_type == "Entire home/apt"
  ) %>% 
  drop_na(rating)
  
```

### Plotly plots: `plot_ly()` make interactive plots

#### scatterplots
```{r}
nyc_airbnb %>% 
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% # "\n": new line
  plot_ly(
    x = ~lat, y = ~long, color = ~price, text = ~text_label, # add text label on the graph
    alpha = 0.5, type = "scatter", mode = "markers")

```

#### boxplots
```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% #reorder `neighbourhood` based on `price`
  plot_ly(x = ~neighbourhood, y = ~price, color = ~neighbourhood,
          type = "box", colors = "viridis")
```

#### violins
```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% #reorder `neighbourhood` based on `price`
  plot_ly(x = ~neighbourhood, y = ~price, color = ~neighbourhood,
          type = "violin", colors = "viridis")
```

#### bar plot
```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% #how many in each `neighbourhood`
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood,
          type = "bar", colors = "viridis")
```

### ggplotly:

```{r}
#plot the ggplot first
ggp_scatter = 
nyc_airbnb %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()

# ggplotly(): make the ggplot also interactive
ggplotly(ggp_scatter) 

#老师觉得这个丑，作业里不能用
```


### create dashboard:

file -> new file -> r markdown -> From Template -> Flex Dashboard -> ok

if has 'css...'  problem, try: `install.packages("htmlwidgets")`
